
\renewcommand{\nompreamble}{
The author has made effort to declare and clarify the following mathematical symbols and notations before entering the main text of this dissertation.
This is to make sure symbols and notations are correct and consistent throughout the dissertation.
On the other hand, sometimes they might look different from how they were defined and used in the original research articles.
}

\makenomenclature
\printnomenclature[2cm]  





\nomenclature{$\Xcal$}{{Domain of training data.}}
\nomenclature{$\Ycal$}{{Multilabel space.}}
\nomenclature{$k$}{{Length of a multilabel.}}
\nomenclature{$j$}{{Index of a microlabel in a multilabel.}}
\nomenclature{$m$}{{Size of training data.}}
\nomenclature{$i$}{{Index of training data.}}
\nomenclature{$\ind{\cdot}$}{{Indicator function.}}
\nomenclature{$\Ycal_j$}{{Microlabel space.}}
\nomenclature{$\vy$}{{Multilabel vector.}}
\nomenclature{$y_j$}{{Microlabel, the $j$'th position in multilabel.}}
\nomenclature{$(x_i,\vy_i)$}{{Example and multilabel pair.}}
\nomenclature{$F$}{{Mapping function from $\Xcal$ to $\Ycal$.}}
\nomenclature{$G$}{{Output graph structure.}}
\nomenclature{$E$}{{Edge set of $G$, revealing potential dependencies.}}
\nomenclature{$V$}{{Vertex set of $G$, corresponding to multilabel.}}
\nomenclature{$\vy_e$}{{Label of edge $e$.}}
\nomenclature{$\vy_{ie}$}{{Label of edge $e$ for the $i$'th example.}}
\nomenclature{$u_j$}{{Possible label of node $j$.}}
\nomenclature{$\vu_e $}{{Possible label of edge $e$.}}
% 2.1
\nomenclature{$\vw$}{{Weight vector.}}
\nomenclature{$\varphi(x,\vy)$}{{Joint feature map of example and label pair $(x,\vy)$.}}
\nomenclature{$\psi(x,\vy)$}{{Compatibility score of $(x,\vy)$.}}
\nomenclature{$\psi_e(x,\vy_e)$}{{Local edge potential/compatibility score of edge $e$ with label $\vy_e$.}}	
\nomenclature{$\phi(x)$}{{Input feature map.}}
\nomenclature{$\Upsilon(\vy)$}{{Output feature map.}}
\nomenclature{$\xi$}{{Slack parameter.}}
\nomenclature{$\ell(\cdot,\cdot)$}{{Loss function.}}
\nomenclature{$\alpha$}{{Dual variable.}}
% 2.2
% 2.3
% 3
\nomenclature{$G^{(t)}$}{{The $t$'th random output graph.}}
\nomenclature{$E^{(t)}$}{{Edge set of the $t$'th random output graph.}}
\nomenclature{$\tilde{G}$}{{Consensus graph.}}
\nomenclature{$\tilde{E}$}{{Edge set of the consensus graph.}}
\nomenclature{$A(\cdot)$}{{Aggregation function.}}
\nomenclature{$F^{(t)}(\cdot)$}{{The $t$'th base learner, graph labeling model.}}	
\nomenclature{$F(\cdot)$}{{Ensemble model in general form.}}
% 3.1
\nomenclature{$\Gcal$}{{A set of random output graphs.}}	
% 3.2
\nomenclature{$\psi_e^{(t)}(x,\vu_e)$}{{Local compatibility score of edge $e$ with labeled $\vu_e$ from the $t$'th base learner.}}
\nomenclature{$\Psi_E(x)$}{{Collection of all local edge potentials/compatibility scores.}}	
\nomenclature{$\Psi_E^{(t)}(x)$}{{Collection of all local edge potentials/compatibility scores from the $t$'th base learner.}}	
\nomenclature{$\tilde{\psi}_j(x,u_j)$}{{Maximal marginal of node $j$ with label $u_j$.}}
\nomenclature{$\tilde{\Psi}(x)$}{{Collection of all node max-marginals.}}
\nomenclature{$\tilde{\Psi}^{(t)}(x)$}{{Collection of all node max-marginals from the $t$'th base learner.}}
% 3.3	
\nomenclature{$\bar\mu$}{{Marginal dual variable averaged over ensembles.}}	
\nomenclature{$\mu$}{{Marginal dual variable.}}	
% 3.4
\nomenclature{$\Delta^R_{{\tiny MAM}}(x,\vy)$}{{Reconstruction error from MAM.}}	
\nomenclature{$\Delta^R_{{\tiny I}}(x,\vy)$}{{Reconstruction error from individual base learners.}}	
\nomenclature{$T$}{{Size of ensemble.}}
\nomenclature{$t$}{{Index of individual base learner $t\in\{1,\cdots,T\}$}}
\nomenclature{$\psi_j(x,\vy_j)$}{{Local node potential/compatibility score of node $j$ with label $\vy_j$.}}	
\nomenclature{$\psi_j^{(t)}(x,\vy_j)$}{{Local node potential/compatibility score of node $j$ with label $\vy_j$, from the $t$'th learner.}}
\nomenclature{$\psi^{{\tiny MAM}}(x,\vy)$}{{Compatibility score from MAM ensemble.}}
\nomenclature{$\bar\psi_e(x,\vy_e)$}{{Mean compatibility score of edge $e$ with label $\vy_e$ over ensemble.}}
\nomenclature{$\bar\psi_j(x,\vy_j)$}{{Mean compatibility score of node $j$ being label $y_j$ over ensemble.}}
\nomenclature{$\Psi_j(x,y_j)$}{{Random variable of compatibility score on node $j$, $\Psi_j(x,y_j)=\{\psi^{(1)}_j(x,y_j),\cdots,\psi^{(T)}_j(x,y_j)\}$}.}
\nomenclature{$\psi^*(x,\vy)$}{{True compatibility score.}}
\nomenclature{$\psi_j^*(x,y_j)$}{{True compatibility score of node $j$.}}
