

% Errata list, if you have errors in the publications.
%\errata

%
% icml 2014
\addpublication[conference]{Hongyu Su, Aristides Gionis, Juho Rousu}{Structured Prediction of Network Response}{Proceedings of the $31^{th}$ International Conference on Machine Learning (ICML 2014)}{Beijing, China, 2014. JMLR W{\&}CP volume 32:442-450}{June}{2014}{Copyright 2014 by the authors}{su14a}

\addcontribution{

\citepub{su14a} presents a novel formalism of the network response prediction problem, and proposes a structured output prediction algorithm for the problem.
The proposed algorithm \spin\ captures the contextual information and improves the state-of-the-art models in terms of the prediction performance.

The definition of the problem and the initial modeling idea were developed jointly by the authors.
The author made major contribution to designing the learning framework and the optimization algorithm.
The author implemented the whole learning system including \sdp\ and the \greedy\ inference algorithms.
The author designed and performed the experiments and analyzed the results.
The author joint in the designing and writing the research article.

}
%\adderrata{This is wrong}
\addpublicationpdf{publications/su14a.pdf}



%
% prib2010
\addpublication[conference]{Hongyu Su, Markus Heinonen, Juho Rousu}{Multilabel Classification of Drug-like Molecules via Max-margin Conditional Random Fields}{Proceedings of the $5^{th}$ International Conference on Pattern Recognition in Bioinformatics (PRIB 2010)}{Nijmegen, The Netherlands, 2010. Springer LNBI volume 6282:265-273}{September}{2010}{Copyright 2014 by the authors}{su10}

\addcontribution{

The novelty of \citepub{su10} is to use a structured output prediction model for multilabel molecular activity classification problem.
The new model incorporates the correlation of the output variables into the learning process and surpasses the previous single-label classification approach in terms of the prediction performance.

The original modeling idea was jointly proposed.
The author implemented the learning system that applying the structured output learning algorithm for the task.
The author designed and performed the experiments and analyzed the results.
All author participated in designing and writing the articles.

}
%\adderrata{This is wrong}
\addpublicationpdf{publications/su10.pdf}


%
% prib 2011
\addpublication[conference]{Hongyu Su, Juho Rousu}{Multi-task Drug Bioactivity Classification with Graph Labeling Ensembles}{Proceedings of the $6^{th}$ International Conference on Pattern Recognition in Bioinformatics (PRIB 2011)}{Delft, The Netherlands, 2011. Springer LNBI volume 7035:157-167}{November}{2011}{Copyright 2014 by the authors}{su11}

\addcontribution{

\citepub{su11} extends \citepub{su10} by learning a majority voting ensemble of a set of structured output classifiers built from random output graphs.

The idea of the ensemble learning strategy was jointly developed. 
The author made major contribution to designing the algorithm.
The author implemented the learning system.
The author designed and performed the experiments and analyzed the results.
The article was structured by authors and was written jointly.

}
%\adderrata{This is wrong}
\addpublicationpdf{publications/su11.pdf}

%
% mlj 2014
\addpublication{Hongyu Su, Juho Rousu}{Multilabel Classification through Random Graph Ensembles}{Machine Learning}{Volume, issue, pages, and other detailed information}{Month}{Year}{Copyright 2014 by the authors}{su14b}

\addcontribution{

\citepub{su14b} extends \citepub{su11} in several ways.
It formulates the algorithm proposed in \citepub{su11} as \mve.
It introduces two other aggregation framework (\amm\ and \mam) which perform inference before or after combining multiple structured output classifiers.
The theoretical study in \citepub{su14b} explains the performance of the proposed \mam\ model.
We also evaluate the performance of the proposed models on a set of heterogeneous multilabel prediction problems.

The original idea of generating aggregation strategy for structured output prediction was developed jointly by authors.
The author designed and implemented the learning frameworks and the optimization algorithms.
The author made major contribution to the theorem proposed in the article.
The author designed and conducted the experiments and analyzed the resutls.
The article was structured by authors and was written jointly.

}
%\adderrata{This is wrong}
\addpublicationpdf{publications/su14b.pdf}




%
% nips 2014
\addpublication[conference]{Mario Marchand, Hongyu Su, Emilie Morvant, Juho Rousu, John Shawe-Taylor}{Multilabel Structured Output Learning with Random Spanning Trees of Max-Margin Markov Networks}{Proceedings of the $28^{th}$ Advances in Neural Information Processing Systems (NIPS 2014)}{to appear}{December}{2014}{Copyright 2014 by the authors}{su14c}

\addcontribution{

\citepub{su14c} is a major step forward of \citepub{su14b} by introducing the joint learning and inference framework and developing rigours learning theory to backup the algorithm.

The idea was initialized jointly by the authors.
The author joint the discussion and the development of the theoretical work.
The author made major contribution to the learning framework and optimization algorithms.
The author implemented the whole learning system that brings the theory into practice.
The author designed and performed the experiments and analyzed the results.
All authors participated in designing and writing the research article.

}
%\adderrata{This is wrong}
\addpublicationpdf{publications/su14c.pdf}


\iffalse
%
% mlj 2014
\addpublication{Hongyu Su, Juho Rousu}{Multilabel Classification through Random Graph Ensembles}{Machine Learning}{Volume, issue, pages, and other detailed information}{Month}{Year}{Copyright 2014 by the authors}{su14b}

\addcontribution{

\citepub{su14b} extends \citepub{su13} by adding extensive literature review, details in developing the algorithm, and more experimental results.
It also links the model performance to the existing theory by providing empirical evidence.

The article was designed and written jointly.
The experiments are mostly contributed by the author.

}
%\adderrata{This is wrong}
\addpublicationpdf{publications/su14b.pdf}

%
% acml 2014
\addpublication[conference]{Hongyu Su, Juho Rousu}{Multilabel Classification through Random Graph Ensembles}{Proceedings of the $5^{th}$ Asian Conference on Machine Learning (ACML 2013)}{Canberra, Australia, 2013. JMLR W{\&}CP volume 29:404-418}{November}{2013}{Copyright 2013 by the authors}{su13}

\addcontribution{

\citepub{su13} generalizes \citepub{su11} in several ways.
The article introduces two advanced ensemble frameworks for multilabel structured output prediction, and describes a theory to explain the advantage of the proposed models.
It also extends the application from drug-bioactivity prediction problem to other applications.

The original idea of generating ensembles was developed jointly by authors.
The author developed the algorithms that bring the idea into effect
The theory was mainly developed by the author.
The article was written jointly.

}
%\adderrata{This is wrong}
\addpublicationpdf{publications/su13.pdf}
\fi


