

\begin{preface}[Espoo]

%
First and foremost I wish to express my deep gratitude to Prof. Juho Rousu for supervising my research during the past few years.
None of the these can possibly happen without his enormous and continuous support and encouragement.
%
I am grateful to Prof. John Shawe-Taylor and Prof. Mario Marchand for the brilliant ideas and inspirations during my visits to University College London (UCL) and University Laval.
%
I wish to thank Prof. Aristides Gionis for showing me the hard-working attitude towards research.
My gratitude also goes to my other coauthors Dr. Emile Morvant and Dr. Markus Heinonen. 
%
I thank Dr. Jefrey Lijffijt, Huibin Shen, Dr. Celine Brouard, Dr. Alan Medlar, and Swee Chong Wong for the useful comment during the writing of the thesis.
I would like to thank two pre-examiners Pierre Geurts and Tapio Pahikkala for their valuable comments.
I also thank Prof. Tapio Elomaa for the honour of having him as the opponent of the defense.
%
I gratefully acknowledge the four years funding from Helsinki Doctoral Programme in Computer Science -- advanced computing and intelligent system (Hecse), and the fundings from Academy of Finland (grant 118653) and the EU PASCAL Network of Excellence.
% 
I thank Department of Computer Science in University of Helsinki for the first year of my research in 2011.
I express my gratitude to all my colleagues in Helsinki Institute for Information Technology HIIT, Department of Information and Computer Science (ICS) in Aalto University for the enjoyable and inspiring working environment and the excellent IT support.
%
My special gratitude goes to Chunxiang for her perseverance, endless support and encouragement outside the research.
%
Finally, I am deeply in-debt to my parents Minsheng and Luwei -- for everything.


%The thesis summarizes the work I have carried out mainly at the Helsinki Institute for Information Technology HIIT, the Department of Information and Computer Science (ICS), Aalto University between early 2012 and late 2014.
%Part of the work has been done at the Department of Computer Science, University of Helsinki during the year 2011 when I started as a doctoral student.
%The work has been generously funded by the Helsinki Doctoral Programme in Computer Science (Hecse), the Academy of Finland (Finnish Centre of Excellence in Algorithm and Data Analysis 118653), including the support for attending international conferences and research visits.

%I am lucky to be a part of the research group \textit{Kernel Machine, Pattern Analysis and Computational Biology} led Prof. Rousu.
%I will to thanks all group members I had worked with for the discussion and the inspiration: Esa Pitk\"anen, Markus Heinonen, Huibin Shen, Jana Kludas, 
%Nicole Althermeler, Jefrey Lijffijt, Celine Brouard, Elena Czeizler, Anna Cichonska, Viivi Uurtio. 







\end{preface}
